---
title: "EDPS 845 Assignment 1"
author: "Yage Guo"
---

## Overview

Demonstrate your mastery of concepts and procedures covered in *An Introduction to R*, chapters 1 through 9. See Appendix A for examples.

Complete this assignment by responding to each question below using your own original code, in addition to answering any questions. Follow Google's [R coding conventions](https://google.github.io/styleguide/Rguide.xml), and use [R markdown](http://rmarkdown.rstudio.com/index.html) formatting for your responses, with example R code written as

```{r}
# Comment within some example code
```

Your file should have an Rmd extension, and you should check that it compiles to HTML using the *Knit* command in RStudio (this runs `knitr::knit()` on the file). Note that you can already *Knit* this file to see how it works.

## Exercises

### Chapter 1

1. Show that you can access the home page for the HTML R help menu, as well as help files for individual functions.

```{r}
# Open R help
help.start()

# Check plot function
? plot

```


2. Demonstrate correct and incorrect naming of R objects.
```{r,eval=FALSE}
# Correct naming of object  
score <- 1:5
# Incorrct naming of object
5Zscore <- 1:5

```

3. How do you list all available objects in the R workspace? And how do you remove individual objects?
```{r}
# list objects
ls()
# remove objects
rm(score)
```


### Chapter 2

1. Create and index a vector using a logical, integer, negative integer, and character vector.
```{r}
myvec <- c(3>5,5,-5,"world")

# index the number 5
myvec[2]

```


2. Create a simple data frame containing a numeric variable, character variable, and factor with at least 3 levels. Use the data frame to demonstrate how R codes and handles missing data. 
```{r}

patientID = c(1, 2, 3,rep(NA,3))
diabetes = c("Type1", "Type2", "Type1")
status = c("Poor", "Improved", "Excellent")
status <- as.factor(status)
patientdata = data.frame(patientID, diabetes, status)
patient <- is.na(patientdata$patientID)
patient
sum <- sum(patientdata$patientID, na.rm= TRUE)
```


### Chapter 3

1. Demonstrate how to check and change the modes and attributes of R objects.

```{}
# check and change mode
x <- c(1,2,3)
mode(x)
x <- as.character(x)
mode(x)

# check and change attributes
attributes(patientdata)
attr(patientdata,"names") <- c("ID","type","status")
attributes(patientdata)

```


### Chapter 4

1. Complete the exercise on page 17, where you calculate 95% confidence intervals for state mean incomes.
```{r}
state <- c("tas", "sa", "qld", "nsw", "nsw", "nt", "wa", "wa",
           "qld", "vic", "nsw", "vic", "qld", "qld", "sa", "tas",
           "sa", "nt", "wa", "vic", "qld", "nsw", "nsw", "wa",
           "sa", "act", "nsw", "vic", "vic", "act")
statef <- factor(state)

incomes <- c(60, 49, 40, 61, 64, 60, 59, 54, 62, 69, 70, 42, 56,
             61, 61, 61, 58, 51, 48, 65, 49, 49, 41, 48, 52, 46,
             59, 46, 58, 43)

incmeans <- tapply(incomes, statef, mean)
stderr <- function(x) sqrt(var(x)/length(x))
incster <- tapply(incomes, statef, stderr)

data.frame(i=incomes, s= statef)
ns <- table(statef)
qt(.025, ns - 1)
qt(.025, ns - 1, lower.tail = FALSE)
cis <- data.frame(mean = incmeans, stderr = incster,
                 state= names(incmeans),
                 lower= qt(.025, ns - 1),
                 upper = qt(.025, ns - 1, lower.tail = FALSE))

```


2. In what order are the levels of ordered factors stored in?
```{r}
# The levels of ordered factors are stored in alphabetical order.
```

### Chapter 5

1. Create an array with dimensions `c(3, 6, 2)` and use it to demonstrate array indexing.


```{r}

x <- array(1:36, dim=c(3,6,2))
x
x [1,3,1]

```


2. Create a two dimensional array of 100 integers sampled with replacement from the vector 1:20, and use an index array to set the diagonal values to 0.

```{r}
# Create a random sample
b1 <- sample(1:20, 100, replace= TRUE)
dim(b1) <- c(10, 10)
b1

# Use index array to set diagonal value to 0
x <- array(c(1:10, 1:10), dim=c(10,2))
b1[x] <- 0
b1

```

3. Construct the same array using the `array()` function and using a vector with the `dim()` set. Prove they are the same.

```{r}
# Using array
b2 <- array(sample(1:20, 100, replace= TRUE), dim=c(10,10))
b2
# Using dim
b1 <- sample(1:20, 100, replace= TRUE)
dim(b1) <- c(10, 10)
b1

```

4. Use your array from 5.1, and another with the same dimensions, to demonstrate how arithmetic works with arrays.
```{r}
x <- array(1:36, dim=c(3,6,2))
x2 <- array(2:37, dim=c(3,6,2))
x2
x3 <- x+x2
x3
```

5. Show how to clear the dimensions of an array.

```{r}
# Clear dimension of x from 5.1
vec <- c(x)
vec
```


### Chapter 6

1. Demonstrate the different ways of subsetting a list.
```{r}
mylist <- list(patientID = c(1, 2, 3, 4),age = c(25, 34), status=c("good", "great"))
mylist
mylist$patientID
mylist[["status"]]


```



2. What is the difference between giving multiple lists to `list()` versus `c()`?


```{r}
# When giving multiple lists to list(), the elements of a list can have different types  components .
# When giving multiple lists to function c(), the result is an object of mode list also, whose components are those of the argument lists joined together in sequence.
```

3. How do data frames in R relate to lists?
```{r}
# Data frames are lists of different elements, such as vector, number. The different columns can have different types, but they must have the same length.
# The elements of a list can be any type (even a list) and can be any length. 

```

4. What is the purpose of `attach()`?

```{r}
# The attach() function adds the data frame to the R search path
```

### Chapter 7

1. Demonstrate the different approaches to reading in data from an external file.
```{r,eval=FALSE}

data <- read.csv("~/documents/R Programming/project/STAT.csv")

data(mtcars)

scan()

```


### Chapter 8

1. Demonstrate the use of distribution functions to simulate data and calculate probabilities and quantiles.

```{r}
x <- rnorm(100, mean = 10, sd = 1)
qnorm(p = .01, mean=10, sd=1)
pnorm(q = 2.56, mean=10, sd=1)
```



2. Simulate data from a t distribution and check their normality.

```{r}
x <- rt (n=50, df=21)
hist(x)
shapiro.test(x)

```


### Chapter 9

1. What is the difference between `if() else` and `ifelse()`?
```{r}
#The if-else control structure executes a statement if a given condition is true. A different statement is executed if the condition is false. For example:

i <- 2
if(i == 1){
print("Hello World!")
}else{
print("Goodbye World!")
}

# The ifelse construct is a compact and vectorized version of the if-else construct.The first statement is executed if condition is TRUE. If condition is FALSE, the second statement is executed. For example:
score <- 2
ifelse(score > 0.5, print("Passed"), print("Failed"))

```


2. Demonstrate the use of a `for()` loop.

```{r}
# For-Loop
for(i in 1:30){
print(i)
}


```



