---
  title: "EDPS 845 Assignment 2"
  author: "Yage Guo"
  
---
# Exercises
    
## Chapter 2
    
###   2.13 Exercises
1.	What are the six types of atomic vector? How does a list differ from an atomic vector?
 
```{r}
# Four common types are logical, integer, double and character. The two rarer types are complex and raw. The elements of a list can have different types (even a list); The elements of an atomic vector are all of the same type.

```

2.	What makes is. vector() and is. numeric() fundamentally different to is.list() and is.character()?
```{r}
# is.vector() does not test if an object is a vector. Instead it returns TRUE only if the object is a vector with no attributes apart from names. 
# is.numeric() is a test for the "numberliness" of a vector and returns TRUE for both integer and double vectors. 

# is.list() tests whether an object is truly a list.
# is. character() tests whether an object is truly a character.


```



3. Test your knowledge of vector coercion rules by predicting the output of the following uses of c():

c(1, FALSE)
c("a", 1)
c(list(1), "a")
c(TRUE, 1L)

```{r}

c(1, FALSE)
# integer vector of 1 and 0
c("a", 1)
# character vector of "a" and "1"
c(list(1), "a")
# list, it has a integer vector 1 and a character vector "a"
c(TRUE, 1L)
# integer vector of 1 and 1
```


4  Why do you need to use unlist() to convert a list to an atomic vector? Why doesn't as.vector() work?


```{r}

# We need to use unlist() to convert a list to an atomic vector, as.vector() doesn't work, Because a list is already a vector. 


```


5. Why is 1 == "1" true? Why is -1 < FALSE true? Why is "one" < 2 false?

```{r}
# 1 == "1" is true because 1 is coerced to character "1".
# -1 < FALSE is true because FALSE is coerced to 0, When a logical vector is coerced to an integer, TRUE becomes 1 and FALSE becomes 0. 
# "one" < 2 is false because 2 is coerced to character "2" and "one" greater than the character "2".

```


6. Why is the default missing value, NA, a logical vector? What's special about logical vectors? (Hint: think about c(FALSE, NA_character_).)

```{r}
# In the example, c(FALSE, NA_character_), this coerces all the elements to character.Perhaps logical is the lowest level when Coercing. When define missing value, NA, as a logical vector, it could not coerce other types of vector. 


```


### 2.2.2 Exercises
1.An early draft used this code to illustrate structure():

  structure(1:5, comment = "my attribute")
  #> [1] 1 2 3 4 5
But when you print that object you don't see the comment attribute. Why? Is the attribute missing, or is there something else special about it? (Hint: try using help.)

```{r}
 structure(1:5, comment = "my attribute")
  #> [1] 1 2 3 4 5
attributes(structure)
help(attributes)

#By default, R didn't print the comment attribute. Comment is a special case that is not printed. 

```

2. What happens to a factor when you modify its levels?

f1 <- factor(letters)
levels(f1) <- rev(levels(f1))

```{r}
f1 <- factor(letters)
f1 # It retures a,b,c... and levels a,b,c...
levels(f1) <- rev(levels(f1))
f1 # Modifying its levels reversed both the vector and the levels,it retures z,y,x... and levels z,y,x...


```

3.  What does this code do? How do f2 and f3 differ from f1?

f2 <- rev(factor(letters))

f3 <- factor(letters, levels = rev(letters))

```{r}
f2 <- rev(factor(letters))
f2 # Different from f1, f2 returns z x y ... but still have the same levels a b c ...., because this code only reversed the factor.

f3 <- factor(letters, levels = rev(letters))
f3 # Different from f1, f3 returns a b c ... but levels print z x y ..., because this code reversed the levels of the factor.


```

### 2.3.1 Exercises
1. What does dim() return when applied to a vector?

```{r}
x <- c(1,2,3)
dim(x)
# It will reture NULL, when applied to a vector.

```


2. If is.matrix(x) is TRUE, what will is.array(x) return?

```{r}
x <- matrix(1:6, ncol = 3, nrow = 2)
is.matrix(x)          
is.array(x) # It will return TURE, because matrix is a special case of the array, which has two dimensions. 

```


3. How would you describe the following three objects? What makes them different to 1:5?

  x1 <- array(1:5, c(1, 1, 5))
  x2 <- array(1:5, c(1, 5, 1))
  x3 <- array(1:5, c(5, 1, 1))
  
```{r}
x1 <- array(1:5, c(1, 1, 5))
x2 <- array(1:5, c(1, 5, 1))
x3 <- array(1:5, c(5, 1, 1))

# x1, x2, and x3 are three-dimensional arrays, whereas 1:5 is an atomic vector. x1 is 1 row by 1 column of 5 length; 
# x2 is 1 row by 5 columns of 1 length; x3 is 5 rows by 1 column of 1 length. 

```


### 2.3.5 Exercises
1. What attributes does a data frame possess?

```{r}
# Data frame has names(),rownames(), and class(), for example
x <- data.frame(a=c(2,3),b=c(TRUE, FALSE))
attributes(x)
```


2. What does as.matrix() do when applied to a data frame with columns of different types?

```{r}
x <- data.frame(a=c(2,3),b=c(TRUE, FALSE))
as.matrix(x)
# When as.matrix() do applied to a data frame, the coercion happens, columns of different types become one type. 

```


3. Can you have a data frame with 0 rows? What about 0 columns?
```{r}
# Yes, we can have a data frame with 0 rows and 0 columns, for example:

a <- data.frame()
a

```


### Chapter 3

### 3.1.7 Exercises

1. Fix each of the following common data frame subsetting errors:

mtcars[mtcars$cyl = 4, ]
mtcars[-1:4, ]
mtcars[mtcars$cyl <= 5]
mtcars[mtcars$cyl == 4 | 6, ]
```{r}
# using "==" select values equal to 4
mtcars[mtcars$cyl == 4, ]  
# using vector to remove
mtcars[-c(1:4), ]
# need to select the columns
mtcars[mtcars$cyl <= 5,]

mtcars[mtcars$cyl == 4 |mtcars$cyl ==  6, ]

```

2. Why does x <- 1:5; x[NA] yield five missing values? (Hint: why is it different from x[NA_real_]?)
```{r}
 x <- 1:5 
 x[NA]
 x[NA_real_]
 # NA is a logical vector of length 1, when x <- 1:5, NA is recycled to the length of x, in this case, NA recycled to the length of 5. 

```

3. What does upper.tri() return? How does subsetting a matrix with it work? Do we need any additional subsetting rules to describe its behaviour?

x <- outer(1:5, 1:5, FUN = "*")
x[upper.tri(x)]
```{r}
x <- outer(1:5, 1:5, FUN = "*")
x[upper.tri(x)]

# upper.tri() returns a matrix of logicals the same size of a given matrix with entries TRUE in the upper triangle. When subsetting a matrix with upper.tri(),it will return the values in the upper triangle, column by column.We don't need new subsetting rules.

```

4. Why does mtcars[1:20] return an error? How does it differ from the similar mtcars[1:20, ]?
```{r}
nrow(mtcars)
ncol(mtcars)
# mtcars[1:20], there are only 11 columns, but this code calls for the first 20 columns, so it return an error.
mtcars[1:20,] #it will return the first 20 rows and there are 32 rows in mtcars.

```

5. Implement your own function that extracts the diagonal entries from a matrix (it should behave like diag(x) where x is a matrix).
```{r}
x <- outer(1:5, 1:5, FUN = "*")
diag(x)


extrdiag <- function(x)
{
  a <- min(dim(x))
  select <- vector()
  for(i in 1:a){
    select[i] <- x[i,i]
  }
  return(select)
}

extrdiag(x)

```

6. What does df[is.na(df)] <- 0 do? How does it work?
```{r,eval=FALSE}
df[is.na(df)] <- 0
# It replaces missing values in the data frame by 0. is.na(df) creates a logical df with TRUE and FALSE, if the value returns to TRUE, assign 0 to the missing value; Otherwise, it will have original value. 

```

### 3.2.4 Exercises

1. Given a linear model, e.g., mod <- lm(mpg ~ wt, data = mtcars), extract the residual degrees of freedom. Extract the R squared from the model summary (summary(mod))
```{r}

mod <- lm (mpg~wt, data = mtcars)
str(mod)

# Extract the R squared from the model summary
summary(mod)$r.squared
# Extract the residual degrees of freedom
mod$residuals

```


### 3.4.9 Exercises

1. How would you randomly permute the columns of a data frame? (This is an important technique in random forests.) Can you simultaneously permute the rows and columns in one step?
```{r}
mydat <- data.frame(x = 1:3, y = 4:6, z =7:9)

# Randomly sample of columns
mydat[sample(ncol(mydat))]
mydat[sample(nrow(mydat))]

# Permute the rows and columns in one step
mydat[sample(nrow(mydat)), sample(ncol(mydat))]


```

2. How would you select a random sample of m rows from a data frame? What if the sample had to be contiguous (i.e., with an initial row, a final row, and every row in between)?
```{r}
mydat <- data.frame(x = 1:3, y = 4:6, z =7:9)
# Random sample of m rows
sample(nrow(mydat),2)

```

3. How could you put the columns in a data frame in alphabetical order?
```{r}
#  Put the columns of mtcars in alphabetical order
mtcars[order(names(mtcars))]

```

## Chapter 6   

### 6.1.2 Exercises
1. What function allows you to tell if an object is a function? 
   What function allows you to tell if a function is a primitive function?

```{r}
str(mean)

get("mean")

# is.function() tells whether an object is a function
is.function(mean)

# is.primitive() tells whether an object is a primitive function
is.primitive(mean)

```

2. This code makes a list of all functions in the base package.
	 objs <- mget(ls("package:base"), inherits = TRUE)
   funs <- Filter(is.function, objs)
   Use it to answer the following questions:
   
   a.	Which base function has the most arguments?

```{r}
objs <- mget(ls("package:base"), inherits = TRUE)
funs <- Filter(is.function, objs)

# Using sapply
argus  <- sapply (funs, function(x) length(formals(x)))
n_most <- which.max(argus)                                   
n_most

# The function of scan() has the most arguments.
```
   
   
   b.	How many base functions have no arguments? What's special about those functions?
```{r}
argus  <- sapply (funs, function(x) length(formals(x)))
length(no_arg <- which(argus == 0))
head(no_arg)

# Returns 225 base functions have no arguments. It seems like most of them are primitive functions. 

```

   
   c.	How could you adapt the code to find all primitive functions?
```{r}
# The previous question provides funs <- Filter(is.function, objs), after adapting the code: 

Filter(is.primitive, objs)

```

3.	What are the three important components of a function?
```{r}
# The three components of a function are body(), the code inside the function; formals(), the list of arguments; and environment(), the location of the function's variables.

```
4. When does printing a function not show what environment it was created in?

```{r}
# When the function is created in the global environment, then printing a function will not show.
```


# 6.2.5 Exercises

1.	What does the following code return? Why? What does each of the three c's mean?
	 c <- 10
   c(c = c)
   
   
```{r}
 c <- 10
 c(c = c)
# It returns a numeric vector with the value 10, named "c".
# 1st is a concatenate function, 2nd is a name related to the right side of the equal sign, 3rd is a object with the value 10. 

```

2.	What are the four principles that govern how R looks for values?

```{r}
# 1 Name masking: R will use the most recent assignment to name things.
# 2 Functions vs. variables: R knows what are you looking for, if you are using a name in a context, R knows you want a function, the R will ignore objects while it is searching. 
# 3 A fresh start: every time a function is called, a new environment is created to host execution.
# 4 Dynamic lookup: R looks for values that have recently been assigned. 


```


3.	What does the following function return? Make a prediction before running the code yourself.
	f <- function(x) {
  	f <- function(x) {
    	f <- function(x) {
      	   x ^ 2
      	  }
    	    f(x) + 1
    	  }
  	    f(x) * 2
       }
   f(10)
```{r}
# Predicting the returns ((10 ^ 2) + 1) * 2 = 202, it matches with the return. 

	f <- function(x) {
  	f <- function(x) {
    	f <- function(x) {
      	   x ^ 2
      	  }
    	    f(x) + 1
    	  }
  	    f(x) * 2
       }
   f(10)
   

```


# 6.4.6 Exercises

1.	Clarify the following list of odd function calls:
  	x <- sample(replace = TRUE, 20, x = c(1:10, NA))
    y <- runif(min = 0, max = 1, 20)
    cor(m = "k", y = y, u = "p", x = x)

```{r}
# x <- sample(replace = TRUE, 20, x = c(1:10, NA))

x <- sample(c(1:10, NA), size=20, replace = TRUE)

# y <- runif(min = 0, max = 1, 20)

y <- runif(n=20, min=0, max=1)

# cor(m = "k", y = y, u = "p", x = x)

cor(x, y, method="kendall", use="pairwise")

```



2.	What does this function return? Why? Which principle does it illustrate?
 	  f1 <- function(x = {y <- 1; 2}, y = 0) {
  	  x + y
  	}
    f1()
    
```{r}
 f1 <- function(x = {y <- 1; 2}, y = 0) {
  	  x + y
  	}
    f1()
# This function returns 3, because it evaluates x = {y <- 1; 2} which y begin with the value of 0. This illustrate principle of name masking.
    
```

3.	What does this function return? Why? Which principle does it illustrate?
	  f2 <- function(x = z) {
  	z <- 100
  	x
  	}
    f2()

```{r}
 f2 <- function(x = z) {
  	z <- 100
  	x
  	}
    f2()
# This function returns 100 because it takes z as an argument, z is assigned value of 100, then returns x which according to the function = z.This illustrate principle of dynamic lookup. 
```

#   6.5.3 Exercises
1.	Create a list of all the replacement functions found in the base package. Which ones are primitive functions?
    
```{r}
pri_fun <- mget(ls("package:base"), inherits = TRUE)
x <- Filter(is.primitive, pri_fun)
x

```

2.	What are valid names for user-created infix functions?
```{r}
# All user created infix functions names must start and end with %. 
```


3.	Create an infix xor() operator.


```{r}

x <- c(TRUE, TRUE, FALSE, FALSE)
y <- c(TRUE, FALSE, TRUE, FALSE)

"%xor%" <- function(x, y) xor(x, y)

x %xor% y  
  
```



4.	Create infix versions of the set functions intersect(), union(), and setdiff().

```{r}
"%inter%" <- function(a, b) intersect(a, b)

letters[1:4] %inter% letters[2:5]


"%union%" <- function(a, b) union(a, b)

letters[2:6] %union% letters[3:7]


"%setdi%"  <- function(a, b) setdiff(a, b)

letters[3:7] %setdi% letters[4:8]


```

5.	Create a replacement function that modifies a random location in a vector.

```{r}

"modirandom<-" <- function(x, value) {
  position <- sample(runif(1, max = length(x)))
  x[position] <- value
  x
}

x<-seq(1:10)
modirandom(x) <- 15
x

```



###    6.6.2 Exercises

1.	How does the chdir parameter of source() compare to in_dir()?      
    Why might you prefer one approach to the other?
    
```{r}
# chdir temporarily changes the working directory from within the source() function.
# in_dir() can specify a temporary directory to replace the current working directory. 

```


2.	What function undoes the action of library()? How do you save and restore the values of options() and par()?
    
```{r}
# detach() can undoes the action of library(), for example,
library(ggplot2)
detach(package:ggplot2)

# options() and par(), assign them to an object when using new parameters, and it will save the previous settings

# save options values
sav_opt <- options()

# restore options values
options(sav_opt)

# save par values
sav_par <- par()

# restore par values
par(sav_par)


```

3.	Write a function that opens a graphics device, runs the supplied code, and closes the graphics device (always, regardless of whether or not the plotting code worked).
```{r,eval=FALSE}

graph_fun <- function()
{
  x <- 1:25
  y <- runif(25)
  graph_fun(x, y)
  on.exit(dev.off())
}

graph_fun()

```
4.	We can use on.exit() to implement a simple version of capture.output().
    capture.output2 <- function(code) {
  	  temp <- tempfile()
  	  on.exit(file.remove(temp), add = TRUE)
  	
  	  sink(temp)
      on.exit(sink(), add = TRUE)
  	
  	  force(code)
  	  readLines(temp)
  	}
  	capture.output2(cat("a", "b", "c", sep = "\n"))
    #> [1] "a" "b" "c"

Compare capture.output() to capture.output2(). How do the functions differ? What features have I removed to make the key ideas easier to see? How have I rewritten the key ideas to be easier to understand?
```{r}

# It seems like capture.output2() has few codes, if statements were removed and on.exit() function was added in. This feature makes it easier to understand than capture.output(). 

```



